---
title: "Preprocessing: source to raw data"
author: "Marton Kovacs"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

The source dataset will not be shared because it contains ip addresses of the respondents. All data preprocessing methods that were used to create the raw dataset from the source dataset were done by using the following script.

## Loading data

```{r}
source <- read_csv(here::here("data/source/Dissertation Extraction – Copy_December 8, 2022_20.38.csv"))
```

## Clean variable names

```{r}
source <- janitor::clean_names(source)
```

## Removing Qualtrics labels

```{r}
label <-
  source %>% 
  slice(1:2)

source <-
  source %>% 
  slice(-(1:2))
```

## Creating a simple codebook

```{r}
codebook <-
  label %>% 
  slice(1) %>% 
  pivot_longer(cols = everything(), names_to = "original_var_name", values_to = "description") %>% 
  mutate(
    new_var_name = case_when(
      original_var_name == "q1_0"       ~ "rater_id",
      original_var_name == "q1_0_3_text"       ~ "empty_col",
      original_var_name == "q24"       ~ "form_id",
      original_var_name == "q1_1"       ~ "country",
      original_var_name == "q1_2"       ~ "origin_org",
      original_var_name == "q1_3"       ~ "name_org",
      original_var_name == "q1_3_1"       ~ "rank_org",
      original_var_name == "q1_4"       ~ "risk_level",
      original_var_name == "q1_4_4_text"       ~ "risk_level_text",
      original_var_name == "q1_5"       ~ "field_choice",
      original_var_name == "q1_5_1"       ~ "field_text",
      original_var_name == "q1_6"       ~ "sample_size",
      original_var_name == "q1_7"       ~ "justification",
      original_var_name == "q1_8"         ~ "calculations",
      original_var_name == "q1_9"        ~ "minimal_effect_size",
      original_var_name == "q1_10"        ~ "data_management_plan",
      original_var_name == "q19"        ~ "archived_data",
      original_var_name == "q20"      ~ "open_data",
      original_var_name == "q1_11_1"        ~ "registration_other",
      original_var_name == "q1_11_2"        ~ "registration_clinical_trials",
      original_var_name == "q1_13" ~ "comments",
      TRUE ~ original_var_name
      )
    )

# Save the codebook
readr::write_csv(codebook, here("data/source/sse_source_codebook.csv"))
```

## Variable renaming

We are assigning the new variable names to the source data table using the codebook.

```{r}
colnames(source) <- dplyr::recode(
  colnames(source), 
  !!!setNames(as.character(codebook$new_var_name), codebook$original_var_name)
)

colnames(source)
```

## Deleting columns containing confidential information

```{r}
source <- 
  source %>% 
  select(-ip_address)
```

## Save raw dataset

```{r}
readr::write_csv(source, here("data/raw/sse_raw_data.csv"))
```
